%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research \& Experience}

\workplace{Project Viva--PFAS Mixtures and Child Metabolic Health}{September 2018 – Present}\\
\position{Graduate Student Researcher}{Berkeley, CA}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Sharon Sagiv, PhD \& Patrick Bradshaw, MS, PhD
\item Chemicals mixtures analysis of prenatal per-fluoroalkyl substance (PFAS) exposure.
\item Outcomes of interest include child metabolic health at ages 7-11 (adiposity, adiponectin, leptin, insulin resistance).
\item Used a Bayesian hierarchical modeling framework to account for correlated exposures and missing data.
\end{tightemize}
\sectionsep

\workplace{Case-Control Simulation Project}{December 2017 – Present}\\
\position{Graduate Student Researcher}{Berkeley, CA}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Jennifer Ahern, PhD, MPH.
\item Designed a simulation to look at the biases associated with drawing control groups from complex survey samples for case-control studies.
\item Looked at biases associated with different methods of control sampling (density, cumulative) from various survey designs (clustered, stratified, etc.).
\item Set up simulation for parallel computation to run many iterations of the simulation at once.
\end{tightemize}
\sectionsep

\workplace{Strong Children's Research Center}{May 2018 – August 2018}\\
\position{Summer Intern}{Rochester, NY}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Stephen Cook, MD, MPH.
\item Summer research project assessing the weight trajectory of children preceding enrollment in a weight-loss RCT.
\item Geo-coded and analyzed address data in R to assess the prevalence of food insecurity and child care needs of families served by an outpatient pediatric clinic in Rochester, NY.
\end{tightemize}
\sectionsep

\workplace{Colorectal Cancer and Reproductive History}{July 2017 – May 2018}\\
\position{Graduate Student Researcher}{Berkeley, CA}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Patrick Bradshaw, MS, PhD.
\item Conducted matched logistic regression, multinomial logistic regression, and meta-analysis on women in the Colon Cancer Family Registry Dataset.
\item Looked at reproductive history factors (hormonal birth control use, hormone replacement therapy, etc.) on colorectal cancer incidence, including incidence by tumor subtype.
\end{tightemize}
\sectionsep


\workplace{Strong Children's Research Center}{May 2016 – August 2016}\\
\position{Summer Intern}{Rochester, NY}
%\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Stephen Cook, MD, MPH.
\item Summer research project on the effects and management of food insecurity in children and families.
\item Conducted a review of past literature and analyzed retrospective cross-sectional survey data and demographic data using multivariable logistic regression.
\item Presented findings and proposed solutions to the medical center, key community organizations, and at a national pediatrics meeting.
\end{tightemize}
\sectionsep
\sectionsep
\workplace{Stahl Lab}{August 2014 – May 2017} \\
\position{Undergraduate Researcher}{Berkeley, CA}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Mentorship under Kevin Tharp, PhD \& Andreas Stahl, PhD.
\item Investigated the effects of bioengineered brown adipose tissue implants (BAT-MACT) using a mouse model.
\item Explored the binding interactions of alpha-10 human integrin in preparation for the potential application of brown adipose tissue implants as a therapeutic for obesity.
\item Ran western blots to look at the relationship between actomyosin and brown adipose tissue.
\end{tightemize}
\sectionsep

\workplace{LEAP Institute, San Mateo Medical Center }{July 2014 – August 2014} \\
\position{Summer Intern}{San Mateo, CA}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked to implement the principles of lean enterprise in healthcare departments at San Mateo Medical Center with the goal of reducing waste and cost in the hospital system.
\item Focused specifically on the acute psychiatric ward.
\item Transcribed, analyzed, and cleaned data, assisted with office work, observed meetings at all levels of the hospital in efforts to implement lean.
\end{tightemize}

\sectionsep