%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   PUBLICATIONS AND PRESENTATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications \& Presentations}
\begin{itemize}[leftmargin = 0cm]
\item [] {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, S. Sagiv, P.T. Bradshaw. The Impact of Exposure to Perflouroalkyl Substance Mixtures on Child Metabolic Health.  {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-LigIta} In Preparation}
\item [] {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, E. C. Matthay, C. Rowe, P.T. Bradshaw, J. Ahern. Conducting Case-Control Studies using Survey Data with Complex Sampling Designs: A Simulation Study. {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-LigIta} Submitted}
\item [] {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, E. C. Matthay, C. Rowe, P.T. Bradshaw, J. Ahern. Conducting Case-Control Studies using Survey Data with Complex Sampling Designs: A Simulation Study. Oral presentation at the 51\textsuperscript{st} Annual Meeting for the Society for Epidemiologic Research, Baltimore, MD, June 21, 2018.
\item []M. Mattiucci, {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, S. R. Cook. Food Insecurity and the WE-CARE Survey. Oral presentation by M. Mattiucci at the Pediatric Academic Societies annual meeting, Toronto, Can. May 6, 2018.
\item [] K. M. Tharp, M.S. Kang, G. A. Timblin, J. Dempersmier, G. E. Dempsey, P. H. Zushin, J. Benavides, C. Choi, {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, A. K. Jha, S. Kajimura, K. E. Healy, H. S. Sul, K. Saijo, S. Kumar, A. Stahl. Actomyosin-mediated tension orchestrates uncoupled respiration in adipose tissues. {\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-LigIta} Cell Metabolism} 27, 602–615.e4, 2018.
\item []{\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, K. M. Tharp, A. Stahl. Exploring the Impact of Bioengineered Brown Adipose Tissue Implants in a Mouse Model. Public Health Undergraduate Honors Thesis.  Presented May 2017.
\item []{\fontspec[Path = fonts/NiveauGrotesk/]{Niveau-Med} C. X. Li}, K. DiBitetto, S. R. Cook. The WE-CARE Survey and Food Insecurity. Poster presented at the Pediatric Academic Societies annual meeting, San Francisco, CA. May 6-9, 2017.

\end{itemize}


\sectionsep 