%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TEACHING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Teaching}

\workplace{Introduction to Human Nutrition (NUSCTX 10)}{August 2018 – December 2018}\\
\position{Graduate Student Instructor}{Berkeley, CA}
\begin{tightemize}
\item Taught 3 discussion sections of 30 students (95 students total) for 1 hour/week and held office hours 1-2 hours/week.
\item Lectured on current topics in nutrition including food insecurity, nutrition research, and food technology.
\item Created course materials including worksheets, lecture slides, and exam questions.
\item Calculated midterm and final exam summary statistics and implemented final grade distribution for the course.
\end{tightemize}
\sectionsep

\workplace{Intro to Surgery DeCal}{July 2016 – May 2017}\\
\position{Course Creator/Course Facilitator}{Berkeley, CA}
\begin{tightemize}
\item Developed curriculum inspired by the Shumway Surgical Skills Summer Internship offered at Stanford School of Medicine.
\item Taught students basic surgical techniques through hands-on workshops.
\item Discussed innovation and development, both past and present, in the field of surgery.
\item Helped lead a team of teaching assistants to discuss best practices in teaching surgical technique and possible improvements to the curriculum.
\end{tightemize}
\sectionsep

\begin{comment}
\workplace{Asian Health Services}{January 2016 – May 2017}\\
\position{Labor Coach}{Oakland, CA}
\begin{tightemize}
\item Assist families with limited English proficiency during childbirth as a patient advocate and translator.
\item Champion importance of communication between patients and healthcare professionals, especially in addressing cultural needs and customs.
\end{tightemize}
\sectionsep
\end{comment}

\workplace{Issues: Berkeley Medical Journal DeCal}{September 2015 – May 2017}\\
\position{Course Facilitator}{Berkeley, CA}
\begin{tightemize}
\item Writer (from August 2013), Editor (from August 2014), and Course Facilitator (from May 2015).
\item Taught and provided mentorship to students unfamiliar with scientific journalism, with a focus on topics relating to novel research in medicine, biotechnology, and public health.
\item Worked with students to translate research presented in complex scientific studies into material understandable by the general UC Berkeley population.
%\item Two articles published in Spring 2014 issue, one article published in Fall 2013 issue
\end{tightemize}
\sectionsep 